Data Responsive-report

### 2021-02-16 GALI_2020.Rmd
mixed model analysis

#Normalize NES data (all data is based on a scale from 1 to 5)
preproc_nes <- preProcess(gem_nes[,(4:5)], method=c("range"))
gem_nes <- predict(preproc_nes, gem_nes)

@@

```{r}
gem_aps <- import("Data/GEM-APS.csv")
#Clean and tidy gem APS
gem_aps <- clean_names(gem_aps)
gem_aps <- gem_aps %>%
  row_to_names(row_number = 2)
gem_aps[,-2] <- gem_aps[,-2] %>% mutate_if(is.character,as.numeric)
gem_aps <- clean_names(gem_aps)
gem_aps <- gem_aps %>%
  rename(country = economy) %>%
  rename(inst_signaling_aps = high_status_to_successful_entrepreneurs)%>%
  rename(inst_hc_aps = established_business_ownership) %>%
  rename(inst_sc_aps = total_early_stage_entrepreneurial_activity_tea)

#All APS data is a percentage. We devide by 100 to gat [0,1] range
gem_aps$inst_signaling_gem <- gem_aps$inst_signaling_aps /100
gem_aps$inst_hc_aps <- gem_aps$inst_hc_aps /100
gem_aps$inst_sc_gem <- gem_aps$inst_sc_aps /100

@@

```{r}
#join nes and aps on country and year 
gem <- left_join(gem_nes, gem_aps, by=c("country", "year", "code"))
gem$inst_hc_gem <- rowMeans(gem[,c("inst_hc_nes", "inst_hc_aps")])

gem <- gem %>%
  select(code, country, year, ends_with('_gem'))

@@

gem <- gem %>%
  group_by(country) %>%
  mutate(inst_fc_gem = mean(inst_fc_gem, na.rm= TRUE),
  inst_hc_gem = mean(inst_hc_gem, na.rm= TRUE),
  inst_sc_gem = mean(inst_sc_gem, na.rm= TRUE),
  inst_signaling_gem = mean(inst_signaling_gem, na.rm= TRUE))

gem <- select(gem, -year)

@@

gci <- filter(gci, `Series Global ID` == "EOSQ089" |
                   `Series Global ID` == "EOSQ425" )
gci <- filter(gci, Edition ==2018 )

@@

gci <- gci %>%
  pivot_wider(names_from = series_global_id, 
              values_from = score)
preproc_gci <- preProcess(gci %>%
                            select(starts_with("EOSQ"))
                          , method=c("range"))
gci <- predict(preproc_gci, gci)

gci$inst_fc_gci <- rowMeans(gci[,c('EOSQ425','EOSQ089')], na.rm = TRUE)

gci <- select(gci, !starts_with('EOSQ'))

@@

```{r}
#Rank 1 shows the most important benefit (highest attention)
#After normalizing, I will substract 1 and take absolute value to make sure higher value in range 0 to 1 goes to higher attention. This is to ensure that country and ventures variables move on the same directions, in order to construct a congurance level.

@@

gali$attention_hc <- 1- round((rowMeans(gali[,
                                  c('accel_ben_rank_business_skills',
                                    'accel_ben_rank_mentorship')],
                              na.rm=TRUE)),2)

@@

gali$attention_sc <- 1- round((rowMeans(gali[,
                                  c('accel_ben_rank_network',
                                'accel_ben_rank_access_entreprene')],
                              na.rm=TRUE)),2)

gali$attention_fc <- 1- round((rowMeans(gali[,
                                c('accel_ben_rank_access_investors',
                                  'accel_ben_rank_direct_funding')],
                              na.rm=TRUE)),2)

#I will then mutiply this by the country index to measure the congruence level
```

#Join all 3 datasets 
```{r}
gali_joined <- left_join(gali, gem, by = "country")

@@

#Checking if the two methods of measring institutional fc are correlated. We want them to be highly correlated 
cor(gali_joined$inst_fc_gem, gali_joined$inst_fc_gci, use="complete.obs")

@@

@@

gali$founder1_grad = ifelse(gali$found_name1_education == "Masters Degree" | 
                              gali$found_name1_education =="PhD" |
                              gali$found_name1_education == "Some graduate degree", 1, 0) 
gali$founder1_grad[is.na(gali$founder1_grad)] <- 0

gali$founder2_grad = ifelse(gali$found_name2_education == "Masters Degree" | 
                              gali$found_name2_education =="PhD" |
                              gali$found_name2_education == "Some graduate degree", 1, 0) 
gali$founder2_grad[is.na(gali$founder2_grad)] <- 0

gali$founder3_grad = ifelse(gali$found_name3_education == "Masters Degree" |
                              gali$found_name3_education =="PhD" |
                              gali$found_name3_education == "Some graduate degree", 1, 0)
gali$founder3_grad[is.na(gali$founder3_grad)] <- 0

gali$nb_of_founders <- gali$found_name1_present + gali$found_name2_present + gali$found_name3_present

gali <- filter(gali, nb_of_founders > 0)

gali$grad_pct = ((gali$founder1_grad + gali$founder2_grad + gali$founder3_grad) / gali$nb_of_founders)

@@

gali$founder1_job1_clevel = ifelse(is.na(gali$found_name1_job1_role) | gali$found_name1_job1_role !=  "CEO/Executive Director" , 0, 1)
gali$founder1_job2_clevel = ifelse(is.na(gali$found_name1_job2_role) | gali$found_name1_job2_role !=  "CEO/Executive Director" , 0, 1)
gali$founder2_job1_clevel = ifelse(is.na(gali$found_name2_job1_role) | gali$found_name2_job1_role !=  "CEO/Executive Director" , 0, 1)
gali$founder2_job2_clevel = ifelse(is.na(gali$found_name2_job2_role) | gali$found_name2_job2_role !=  "CEO/Executive Director" , 0, 1)
gali$founder3_job1_clevel = ifelse(is.na(gali$found_name3_job1_role) | gali$found_name3_job1_role !=  "CEO/Executive Director" , 0, 1)
gali$founder3_job2_clevel = ifelse(is.na(gali$found_name3_job2_role) | gali$found_name3_job2_role !=  "CEO/Executive Director" , 0, 1)

gali$prior_clevel_pct = ((gali$founder1_job1_clevel + gali$founder1_job2_clevel + gali$founder2_job1_clevel + 
  gali$founder2_job2_clevel + gali$founder3_job1_clevel + gali$founder3_job2_clevel) / (gali$nb_of_founders*2))

@@

gali$avg_teamtenure <- rowMeans(subset(gali, select = c('found_name1_job1_tenure', 'found_name1_job2_tenure', 'found_name2_job1_tenure', 'found_name2_job2_tenure', 'found_name3_job1_tenure', 'found_name3_job2_tenure')), na.rm = TRUE)

gali$avg_teamtenure[is.nan(gali$avg_teamtenure)] <- 0

#Team Prior Founding
gali$team_prior_founding <- gali$found_name1_prior_fp + gali$found_name2_prior_fp + gali$found_name3_prior_fp + gali$found_name1_prior_other + gali$found_name2_prior_other + gali$found_name3_prior_other + gali$found_name1_prior_np + gali$found_name2_prior_np + gali$found_name3_prior_np

@@

gali$z_team_prior_founding <- scale(gali$team_prior_founding, center = TRUE, scale = TRUE)
gali$z_prior_clevel_pct <- scale(gali$prior_clevel_pct, center = TRUE, scale = TRUE)
gali$z_avg_teamtenure <- scale(gali$avg_teamtenure, center = TRUE, scale = TRUE)
gali$z_grad_pct <- scale(gali$grad_pct, center = TRUE, scale = TRUE)

@@

gali$normq_team_prior_founding <- normalize.quantiles(gali$z_team_prior_founding,copy=TRUE)
gali$normq_prior_clevel_pct <- normalize.quantiles(gali$z_prior_clevel_pct,copy=TRUE)
gali$normq_avg_teamtenure <- normalize.quantiles(gali$z_avg_teamtenure,copy=TRUE)
gali$normq_grad_pct <- normalize.quantiles(gali$z_grad_pct,copy=TRUE)

@@

gali$HC_index <- (gali$normq_team_prior_founding + gali$normq_prior_clevel_pct + gali$normq_avg_teamtenure + gali$normq_grad_pct)

>>>>

#Normalize NES data (all data is based on a scale from 1 to 5)
preproc_nes <- preProcess(gem_nes[,(4:5)], method=c("range"))

gem_nes <- predict(preproc_nes, gem_nes)

@@

```{r}
#gem_aps <- import("Data/GEM-APS.csv")
#Clean and tidy gem APS
#gem_aps <- clean_names(gem_aps)
#gem_aps <- gem_aps %>%
  #row_to_names(row_number = 2)
#gem_aps[,-2] <- gem_aps[,-2] %>% mutate_if(is.character,as.numeric)
#gem_aps <- clean_names(gem_aps)
#gem_aps <- gem_aps %>%
  #rename(country = economy) %>%
  #rename(inst_signaling_aps = high_status_to_successful_entrepreneurs) #%>%
  #rename(inst_hc_aps = established_business_ownership) %>%
  #rename(inst_sc_aps = total_early_stage_entrepreneurial_activity_tea)

#All APS data is a percentage. We devide by 100 to gat [0,1] range
#gem_aps$inst_signaling_gem <- gem_aps$inst_signaling_aps /100 
#gem_aps$inst_hc_aps <- gem_aps$inst_hc_aps /100 + 1
#gem_aps$inst_sc_gem <- gem_aps$inst_sc_aps /100 + 1

@@

```{r}
gem <- gem_nes
#join nes and aps on country and year 
#gem <- left_join(gem_nes, gem_aps, by=c("country", "year", "code"))
#gem$inst_hc_gem <- rowMeans(gem[,c("inst_hc_nes", "inst_hc_aps")]) + 1
#gem$inst_hc_gem <- gem$inst_hc_nes

#gem <- gem %>%
  #select(code, country, year, ends_with('_gem'))

@@

gem <- gem %>%
  group_by(country) %>%
  mutate(inst_fc_gem = mean(inst_fc_gem, na.rm= TRUE))
#  inst_hc_gem = mean(inst_hc_gem, na.rm= TRUE),
  #inst_sc_gem = mean(inst_sc_gem, na.rm= TRUE),
#  inst_signaling_gem = mean(inst_signaling_gem, na.rm= TRUE))

#gem <- select(gem, -year, -inst_hc_nes)

@@

gci <- filter(gci, `Series Global ID` == "EOSQ089" |
                   `Series Global ID` == "EOSQ425" |
                   `Series Global ID` == "EOSQ109")
gci <- filter(gci, Edition ==2018 )

@@

gci <- gci %>%
  pivot_wider(names_from = series_global_id, 
              values_from = score)

#preproc_gci <- preProcess(gci %>%
#                           select(starts_with("EOSQ"))
#                          , method=c("range"))
#gci <- predict(preproc_gci, gci)

#gci$inst_fc_gci <- rowMeans(gci[,c('EOSQ425','EOSQ089')], na.rm = TRUE)

#gci$inst_sc_gci <- gci$EOSQ109

#gci <- select(gci, !starts_with('EOSQ'))

@@

```{r}
#Rank 1 shows the most important benefit (highest attention)

@@

gali$attention_hc <- 1- round(gali$accel_ben_rank_business_skills,2)

@@

gali$attention_sc <- 1- round((rowMeans(gali[,
                                  c('accel_ben_rank_network',
                                'accel_ben_rank_access_entreprene',
                                'accel_ben_rank_access_investors')],
                              na.rm=TRUE)),2)

gali$attention_fc <- 1- round(gali$accel_ben_rank_direct_funding,2)

#Join all 3 datasets 
```{r}
gali_joined <- left_join(gali, gem, by = c("country", "year"))

@@

@@

#Mixed model analysis 
```{r}
fit0 <- lmer(capital_raised_tot ~  attention_fc + (attention_fc|country), data = gali_joined, REML = F)

fit1 <- lmer(capital_raised_tot ~ attention_fc + attention_fc*EOSQ425 + (1 |country), data = gali_joined, REML = F)

fit2 <- lmer(capital_raised_tot ~ attention_fc + attention_fc*EOSQ089 + (1 |country), data = gali_joined, REML = F)

fit3 <- lmer(capital_raised_tot ~ attention_fc + attention_fc*inst_fc_gem + (1 |country), data = gali_joined, REML = F)

summary(fit2)

@@

gali_joined$founder1_grad = ifelse(gali_joined$found_name1_education == "Masters Degree" | 
                              gali_joined$found_name1_education =="PhD" |
                              gali_joined$found_name1_education == "Some graduate degree", 1, 0) 
gali_joined$founder1_grad[is.na(gali_joined$founder1_grad)] <- 0

gali_joined$founder2_grad = ifelse(gali_joined$found_name2_education == "Masters Degree" | 
                              gali_joined$found_name2_education =="PhD" |
                              gali_joined$found_name2_education == "Some graduate degree", 1, 0) 
gali_joined$founder2_grad[is.na(gali_joined$founder2_grad)] <- 0

gali_joined$founder3_grad = ifelse(gali_joined$found_name3_education == "Masters Degree" |
                              gali_joined$found_name3_education =="PhD" |
                              gali_joined$found_name3_education == "Some graduate degree", 1, 0)
gali_joined$founder3_grad[is.na(gali_joined$founder3_grad)] <- 0

gali_joined$nb_of_founders <- gali_joined$found_name1_present + gali_joined$found_name2_present + gali_joined$found_name3_present

gali_joined <- filter(gali_joined, nb_of_founders > 0)

gali_joined$grad_pct = ((gali_joined$founder1_grad + gali_joined$founder2_grad + gali_joined$founder3_grad) / gali_joined$nb_of_founders)

@@

gali_joined$founder1_job1_clevel = ifelse(is.na(gali_joined$found_name1_job1_role) | gali_joined$found_name1_job1_role !=  "CEO/Executive Director" , 0, 1)
gali_joined$founder1_job2_clevel = ifelse(is.na(gali_joined$found_name1_job2_role) | gali_joined$found_name1_job2_role !=  "CEO/Executive Director" , 0, 1)
gali_joined$founder2_job1_clevel = ifelse(is.na(gali_joined$found_name2_job1_role) | gali_joined$found_name2_job1_role !=  "CEO/Executive Director" , 0, 1)
gali_joined$founder2_job2_clevel = ifelse(is.na(gali_joined$found_name2_job2_role) | gali_joined$found_name2_job2_role !=  "CEO/Executive Director" , 0, 1)
gali_joined$founder3_job1_clevel = ifelse(is.na(gali_joined$found_name3_job1_role) | gali_joined$found_name3_job1_role !=  "CEO/Executive Director" , 0, 1)
gali_joined$founder3_job2_clevel = ifelse(is.na(gali_joined$found_name3_job2_role) | gali_joined$found_name3_job2_role !=  "CEO/Executive Director" , 0, 1)

gali_joined$prior_clevel_pct = ((gali_joined$founder1_job1_clevel + gali_joined$founder1_job2_clevel + gali_joined$founder2_job1_clevel + 
  gali_joined$founder2_job2_clevel + gali_joined$founder3_job1_clevel + gali_joined$founder3_job2_clevel) / (gali_joined$nb_of_founders*2))

@@

gali_joined$avg_teamtenure <- rowMeans(subset(gali_joined, select = c('found_name1_job1_tenure', 'found_name1_job2_tenure', 'found_name2_job1_tenure', 'found_name2_job2_tenure', 'found_name3_job1_tenure', 'found_name3_job2_tenure')), na.rm = TRUE)

gali_joined$avg_teamtenure[is.nan(gali_joined$avg_teamtenure)] <- 0

#Team Prior Founding
gali_joined$team_prior_founding <- gali_joined$found_name1_prior_fp + gali_joined$found_name2_prior_fp + gali_joined$found_name3_prior_fp + gali_joined$found_name1_prior_other + gali_joined$found_name2_prior_other + gali_joined$found_name3_prior_other + gali_joined$found_name1_prior_np + gali_joined$found_name2_prior_np + gali_joined$found_name3_prior_np

@@

gali_joined$z_team_prior_founding <- scale(gali_joined$team_prior_founding, center = TRUE, scale = TRUE)
gali_joined$z_prior_clevel_pct <- scale(gali_joined$prior_clevel_pct, center = TRUE, scale = TRUE)
gali_joined$z_avg_teamtenure <- scale(gali_joined$avg_teamtenure, center = TRUE, scale = TRUE)
gali_joined$z_grad_pct <- scale(gali_joined$grad_pct, center = TRUE, scale = TRUE)

@@

gali_joined$normq_team_prior_founding <- normalize.quantiles(gali_joined$z_team_prior_founding,copy=TRUE)
gali_joined$normq_prior_clevel_pct <- normalize.quantiles(gali_joined$z_prior_clevel_pct,copy=TRUE)
gali_joined$normq_avg_teamtenure <- normalize.quantiles(gali_joined$z_avg_teamtenure,copy=TRUE)
gali_joined$normq_grad_pct <- normalize.quantiles(gali_joined$z_grad_pct,copy=TRUE)

@@

gali_joined$HC_index <- (gali_joined$normq_team_prior_founding + gali_joined$normq_prior_clevel_pct + gali_joined$normq_avg_teamtenure + gali_joined$normq_grad_pct)
